%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{ltxtable}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}


%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\definecolor{mamad}{RGB}{190,70,70}
\titleformat{\section}{\Large\scshape\raggedright\color{mamad}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}

\definecolor{linkcolour}{RGB}{0,40,120}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}


%debug page outer frames
%\usepackage{showframe}

\renewcommand{\footnoterule}{
  \kern -3pt
  {\color{mamad} \hrule width 2in height 0.5pt}
  \kern 2.6pt
}

\renewcommand{\footnotesize}{\small}
%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Pouyan Hessabi} \\[7.5pt]
\begin{gather}
 Date of Birth: 4 December 1999
 
\begin{align}
     \href{https://pouyanhessabi.github.io/}{\raisebox{-0.05\height}\faGlobe\ pouyanhessabi.github.io}\ $|$  \href{mailto:pouyan.hessabi@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ pouyan.hessabi@gmail.com} \ $|$ \  \href{mailto:pohe@aut.ac.ir}{\raisebox{-0.05\height}\faEnvelope \ pohe@aut.ac.ir} \
\end{align}
\end{gather}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	RESEARCH INTEREST
%----------------------------------------------------------------------------------------

\section{Research Interests}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
    \multicolumn{2}{@{}X@{}}{
    \text{Software Engineering, Agile Development, Software Architecture, Requirement Engineering, Applied Machine Learning, Human Factors in Software Engineering}
    } \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Amirkabir University of Technology (Tehran Polytechnic), Tehran, Iran} & \hfill 2018 -  2023 \\[2pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
    \item Bachelor of Science in Computer Engineering, GPA\footnote{My Iran GPA was converted to Standard US GPA with \href{https://gpa.eng.uci.edu/node/241}{this} calculator.}: 3.26/4.0
    % \item Last Two Years Major GPA: 17.13/20 (3.62/4.0)
    \item\textbf{Notable Courses:}
    
    \begin{tabularx}{\linewidth}{@{}X X@{}}
{\renewcommand{\arraystretch}{0.1}}
  \begin{itemize}[leftmargin=*]
    \item BSc. Thesis: 4/4
    \item Internship: 4/4
    \item Software Engineering 2: 4/4
    \item Software Engineering 1: 4/4
  \end{itemize}
  &
  \begin{itemize}[leftmargin=*]
    \item Artificial Intelligence: 4/4
    \item Algorithm Design: 4/4
    \item Startup Development: 4/4
    \item Mobile Programming: 4/4
  \end{itemize} \\
\end{tabularx}
    % \begin{itemize}
        % BSc. Thesis: A+, Internship: A+, Software Engineering 2: A+, Software Engineering 1: A, Principles of Artificial Intelligence: A, Algorithm Design: A, Startup Development: A, Mobile Programming: A
    % \end{itemize} 
    \end{itemize}
    } \\
\textbf{Mofid 2 High School, Tehran, Iran} & \hfill 2014 - 2018 \\[2pt]
% \multicolumn{2}{@{}X@{}}{
    % \begin{itemize}
    \quad \quad Diploma of Education in Mathematics and Physics, GPA: 3.91/4
    % \end{itemize}
    % } \\
\end{tabularx}


%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\section{Work and Research Experiences}

\begin{ltxtable}{\textwidth}{}
\textbf{BSc. Thesis, {\href {https://aut.ac.ir/en}{Amirkabir University of Technology}}, Tehran, Iran} & \hfill Jun 2023 - Sep 2023 \\[3.75 pt]
\multicolumn{2}{@{}p{\textwidth}@{}}{
\begin{itemize}
\item \textbf{Title:} Designing and prototyping disease diagnosis and physician referral system using microservices architecture.
\item Under the supervision of \parbox[t]{0.7\linewidth}{\href{https://scholar.google.com/citations?user=oISEZIUAAAAJ&hl=en&oi=ao}{Prof. Amir Kalbasi}}
\item Designed a healthcare system using microservices architecture that includes disease prediction by given symptoms, mapping diseases to particular expertise, and searching physicians.
\item Involved software design and engineering principles, machine learning and requirement engineering.
\item Implementation technologies: Python, Flask, XGBoost, MySQL, Docker, Git.

 \hfill \href{https://github.com/pouyanhessabi/B.Sc-Project-Healthcare-Microservice}{\raisebox{-0.05\height}\faGithub\ Project Link}
\end{itemize}
} \\
\textbf{APM and Scrum Master, {\href {https://faraadid.com}{Faraadid Company}}, Tehran, Iran \parbox[t]{0.7\linewidth}} & \hfill Apr 2023 - Nov 2023 \\[3.75 pt]
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item Associate product manager of an AI-based platform using computer vision to provide HSE services.
    \item Assisting CEO, PM, CTO, and HR in product discovery, business analytics, business strategy, process engineering, quality assurance, and performance measurement.
    \item Established the Scrum framework, led the Scrum team, and facilitated Scrum events in three teams.
    \end{itemize}
    } \\
\textbf{Java Developer, {\href {https://www.linkedin.com/company/dotin/}{Dotin Company}}, Tehran, Iran} & \hfill Aug 2021 - Mar 2022 \\[3.75 pt]
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item Java developer in a banking company.
    \item Worked on an application involving web development skills such as Java SE, Java EE, Hibernate, XML, HTML/CSS/JS, Oracle, clean code principles, and design patterns.
    \item  Business skills encompassed card management, payment processing, card transactions, and facility installments.
    \end{itemize}
    } 
\end{ltxtable}

%----------------------------------------------------------------------------------------
% Teaching Experience Section
%----------------------------------------------------------------------------------------
\section{Teaching Experiences}
\begin{ltxtable}{\textwidth}{}
\textbf{Head Teaching Assistant, Software Engineering II} & \hfill Spring 2023\\[3.75pt]
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item Under the supervision of {\href{https://scholar.google.com/citations? user=7bpNAlAAAAAJ&hl=en}{Dr Faezeh Gohari}} at Amirkabir University of Technology.
    \item Designing (and grading) assignments and projects related to software process, software analysis and design, and testing. Also preparing lecture videos for the students and teaching in the classes.
    \end{itemize}
    } \\
\textbf{Teaching Assistant, Software Engineering (Software Analysis and Design)} & \hfill Spring 2023 \\[3.75pt]
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item Under the supervision of {\href{https://scholar.google.com/citations?user=oQE-MBQAAAAJ&hl=en&oi=ao}{Dr. Ehsan Alirezaei}} at Amirkabir University of Technology and Tehran University.
    \item Designing (and grading) assignments and projects related to software process, software analysis and design and requirement engineering.
    \end{itemize}
    } \\
\end{ltxtable}

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------% Projects
%----------------------------------------------------------------------------------------------------------------------------------------------------------------%

\section{Top Academic Course Projects}

\begin{ltxtable}{\textwidth}{}
\textbf{Information Retrieval,} Search Engine & \hfill Spring 2022 \\
\multicolumn{2}{@{}p{\textwidth}@{}}{
\begin{itemize}
\item Implemented a search engine by tf-idf approach using Python language.
\hfill \href{https://github.com/pouyanhessabi/Search-Engine-IR-Project}{\raisebox{-0.05\height}\faGithub\ Project Link}
\end{itemize}
} \\
\textbf{Advanced Programming,} Music Player & \hfill Spring 2019 \\
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item Designed and Implemented a basic music player using Java. Supporting features like editing songs in library, managing different playlists and watch friends activities.
    \hfill \href{https://github.com/pouyanhessabi/JPotify-java-spotify}{\raisebox{-0.05\height}\faGithub\ Project Link}
    \end{itemize}
    } \\
\textbf{Data Mining,} Diabetes Prediction & \hfill Spring 2022 \\
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item Implemented and evaluated a simple classifier to determine if given data represent patient's diabetes based on its features, using Python language and XGBoost library.
    \hfill \href{https://github.com/pouyanhessabi/Diabetes-Prediction-DM-Project}{\raisebox{-0.05\height}\faGithub\ Project Link}
    \end{itemize}
    } \\
\textbf{Principles of Artificial Intelligence,} Three Projects & \hfill Spring 2021 \\
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item \textbf{Searching Algorithm:} Implemented searching algorithms, including IDS, BBFS, and A*, from scratch to find optimal paths using Python.
    \item \textbf{Genetic Algorithm:} Implemented a genetic algorithm to solve the Super Mario game using Python. No advanced libraries for genetic algorithms were used.
    \item \textbf{NLP Comment Filtering:} Implemented bigram and n-gram models for comment filtering using Python language with Numpy and Pandas libraries.
    \hfill \href{https://github.com/pouyanhessabi/NLP-Comment-Filtering}{\raisebox{-0.05\height}\faGithub\ Project Link}
    \end{itemize}
    } \\
\textbf{Operating System,} MIT XV6 Operating System & \hfill Fall 2020 \\
\multicolumn{2}{@{}p{\textwidth}@{}}{
    \begin{itemize}
    \item Implemented scheduling and some system calls for XV6 OS using the C language.
    % \parbox[t]{0.7\linewidth}} & \hfill \href{https://github.com/pouyanhessabi/XV6-OS}{\raisebox{-0.05\height}\faGithub\ Project Link} \\[3.75 pt]
    \hfill \href{https://github.com/pouyanhessabi/XV6-OS}{\raisebox{-0.02\height}\faGithub\ Project Link}
    \end{itemize}
    } \\ 
\end{ltxtable}

%----------------------------------------------------------------------------------------
%	Technical Skills
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
   
    
    \textbf{Programming Languages and Web Developement:} Python, Java, C, Kotlin, HTML, CSS, \\ JavaScript, XML \\
   \textbf{Hardware Design Languages:} Arduino, Verilog, VHDL  \\
    \textbf{Database Systems:} MySQL, Oracle \\
    \textbf{Operating Systems:} Windows, Linux(Ubuntu) \\
    \textbf{Miscellaneous} Flask, Spring, Git, Docker, Jira, \LaTeX, REST API, Agile (Scrum/Kanban/XP)
\end{tabularx}
%----------------------------------------------------------------------------------------
%	Award and Honors
%----------------------------------------------------------------------------------------
\section{Awards and Honors}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Nationwide University Entrance Exam} & \hfill 2018 \\[2.5pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
    \item \text{Achieved top 2\% among all applicants of the Nationwide University Entrance Exam (known as Konkour) for BSc. in Mathematics and Engineering (Approximately 150000 applicants)}
    \end{itemize}
    } \\
\textbf{Management of Association of Philosophy and Religion} & \hfill 2022 \\[2.5pt]
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
    \item As the manager of Association of Philosophy and Religion at Amirkabir University of Technology, I was the winner of the award for the best cultural association in the field of Culture and Thought among all universities in the country.
    \end{itemize}
    } \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	Languages
%----------------------------------------------------------------------------------------
\section{Languages}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Perisan &  \normalsize{Native}\\
English  &  \normalsize{Fluent (TOEFL IBT anticipated completion date: 12/30/2023)}\\  
\end{tabularx}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
\section{References}
\textbf{\href{https://scholar.google.com/citations?user=7bpNAlAAAAAJ&hl=en}{Faezeh Gohari:}} Lecturer at Amirkabir University of Technology, Tehran, Iran.
\newline Email: faezeh.gohari@gmail.com \newline
\textbf{\href{https://scholar.google.com/citations?user=a_mSCasAAAAJ&hl=en&oi=ao}{Ali Atghaei:}} Technical Manager of AI Department at Faraadid , Tehran, Iran.
\newline Email: ali.atghaei@gmail.com \newline
\textbf{\href{https://scholar.google.com/citations?user=oISEZIUAAAAJ&hl=en&oi=ao}{Amir Kalbasi:}} Assistant Professor at Amirkabir University of Technology, Tehran, Iran.
\newline Email: kalbasi@aut.ac.ir \newline
\newline
\newline


\begin{center}
    \textbf{All certificates, documents, and other references are available upon request.}
\end{center}


\end{document}